---
title: "Understanding Tucker Carlson's Audience"
subtitle: "Beliefs, Attitudes, and the Effects of an AI-Delivered Factual Intervention — Pilot Report"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Table of Contents"
    theme: flatly
    code-fold: true
    code-tools: true
    embed-resources: true
    fig-width: 8
    fig-height: 5
    fig-dpi: 150
execute:
  warning: false
  message: false
  echo: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(kableExtra)
library(scales)
library(cluster)

# ── Shared theme ──────────────────────────────────────────────────────────────
theme_report <- function() {
  theme_minimal(base_size = 12) +
    theme(
      plot.title    = element_text(face = "bold", size = 13),
      plot.subtitle = element_text(color = "grey40", size = 11),
      axis.title    = element_text(size = 11),
      panel.grid.minor = element_blank(),
      strip.text    = element_text(face = "bold"),
      legend.position = "bottom"
    )
}

pal_main  <- c("#2c7bb6", "#d7191c", "#1a9641", "#fdae61", "#756bb1")
pal_divg  <- c("#d7191c", "#fdae61", "#ffffbf", "#a6d96a", "#1a9641")

# ── Load data ─────────────────────────────────────────────────────────────────
df <- read_csv(
  "data/raw/result_persuasion_PrimePanels_2.17.26.csv",
  show_col_types = FALSE
)

n_total    <- nrow(df)
n_complete <- sum(df[["Interview Status"]] == "Completed", na.rm = TRUE)
df_c       <- df |> filter(`Interview Status` == "Completed")

# ── Column helpers ────────────────────────────────────────────────────────────
# Find column names matching a regex, optionally restricted to those also
# matching a fixed suffix string.
fcol <- function(pattern, data = df, suffix = NULL) {
  nms <- grep(pattern, names(data), value = TRUE, perl = TRUE)
  if (!is.null(suffix)) nms <- grep(suffix, nms, value = TRUE, fixed = TRUE)
  nms
}

# Extract the short human-readable label from a long slider column name.
# "(8.1) Please indicate ... - I trust his analysis ... - Value"
# → "I trust his analysis ..."
short_label <- function(col_name) {
  col_name |>
    str_remove("\\- (Value|Code)$") |>
    str_trim() |>
    str_extract("[^–—-]+$") |>
    str_trim()
}

# ── Pre/post paired t-test helper ────────────────────────────────────────────
paired_stats <- function(pre_cols, post_cols, labels, data = df_c) {
  map2_dfr(pre_cols, post_cols, function(p, q) {
    pre_v  <- suppressWarnings(as.numeric(data[[p]]))
    post_v <- suppressWarnings(as.numeric(data[[q]]))
    ok     <- !is.na(pre_v) & !is.na(post_v)
    n      <- sum(ok)
    if (n < 3) {
      return(tibble(n = n, pre = NA, post = NA, diff = NA, d = NA, p = NA))
    }
    diffs <- post_v[ok] - pre_v[ok]
    tst   <- t.test(post_v[ok], pre_v[ok], paired = TRUE)
    tibble(
      n    = n,
      pre  = round(mean(pre_v[ok]),  1),
      post = round(mean(post_v[ok]), 1),
      diff = round(mean(diffs),      1),
      d    = round(mean(diffs) / sd(diffs), 2),
      p    = tst$p.value
    )
  }) |>
    mutate(Item = labels) |>
    relocate(Item)
}

# ── Significance stars ────────────────────────────────────────────────────────
sig_star <- function(p) {
  case_when(
    p < .001 ~ "***",
    p < .01  ~ "**",
    p < .05  ~ "*",
    p < .10  ~ "†",
    TRUE     ~ ""
  )
}

# ── Formatted pre/post table ─────────────────────────────────────────────────
fmt_pp_table <- function(tbl, caption = NULL) {
  tbl |>
    mutate(
      `Pre M` = pre,
      `Post M` = post,
      `Δ`     = case_when(diff > 0 ~ paste0("+", diff), TRUE ~ as.character(diff)),
      `d`     = d,
      `p`     = paste0(format(round(p, 3), nsmall = 3), " ", sig_star(p))
    ) |>
    select(Item, n, `Pre M`, `Post M`, `Δ`, d, p) |>
    kbl(caption = caption, align = c("l","c","c","c","c","c","l")) |>
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, position = "left") |>
    footnote(
      general = "All scales: 0–100. d = Cohen's d for paired differences. † p<.10, * p<.05, ** p<.01, *** p<.001.",
      general_title = ""
    )
}
```

::: {.callout-warning}
## Pilot Data — Treat All Results as Preliminary
This report is based on **`r n_complete` completed responses** (of `r n_total` total) collected on February 17, 2026.
Statistical results have very low power at this sample size and should be replicated at full scale before drawing conclusions.
:::

---

# 1 Study Overview

This study examines the beliefs, attitudes, and media consumption patterns of self-identified Tucker Carlson viewers. Participants completed a survey that included:

1. **Pre-treatment measures** — demographics, media engagement, conspiracy beliefs, foreign policy attitudes, and feelings toward Israel (Questions 1–12).
2. **An AI-delivered conversation** — participants engaged in a structured dialogue with an AI that provided factual context on Israel-related topics (the experimental manipulation, assigned via block randomization).
3. **Post-treatment measures** — the same attitude batteries administered again to detect opinion change (Questions 18–22), plus open-ended reflections on whether the conversation changed their views.

**Primary outcomes of interest:**

| Domain | Pre | Post |
|---|---|---|
| Carlson credibility | Q8 | Q18 |
| Foreign policy views | Q9 | Q19 |
| Feelings toward Israel/Jewish people | Q10 | Q20 |
| Carlson's Israel commentary | Q11 | Q21 |
| Israel policy positions | Q12 | Q22 |

---

# 2 Sample Characteristics

```{r}
#| label: demo-prep

age_col    <- fcol("^\\(26\\) What is your age")
gender_col <- fcol("^\\(27\\) What is your gender")
race_col   <- fcol("^\\(29\\) What is your race")
ideo_col   <- fcol("^\\(30\\) Do you consider yourself politically")
party_col  <- fcol("^\\(31\\) Do you consider yourself a Democrat")
income_col <- fcol("^\\(32\\) What is your combined")
educ_col   <- fcol("^\\(33\\) What is the highest level")
state_col  <- fcol("^\\(35\\) In what state")

demo <- df_c |>
  transmute(
    age      = .data[[age_col[1]]],
    gender   = .data[[gender_col[1]]],
    race     = .data[[race_col[1]]],
    ideology = .data[[ideo_col[1]]],
    party    = .data[[party_col[1]]],
    income   = .data[[income_col[1]]],
    education = .data[[educ_col[1]]],
    state    = .data[[state_col[1]]]
  )
```

```{r}
#| label: fig-demo
#| fig-height: 9
#| fig-cap: "Demographic profile of completed respondents (n = `r n_complete`)"

demo_long <- bind_rows(
  demo |> count(Category = age,       Variable = "Age"),
  demo |> count(Category = gender,    Variable = "Gender"),
  demo |> count(Category = ideology,  Variable = "Political Ideology"),
  demo |> count(Category = party,     Variable = "Party"),
  demo |> count(Category = income,    Variable = "Household Income"),
  demo |> count(Category = education, Variable = "Education")
) |>
  filter(!is.na(Category)) |>
  group_by(Variable) |>
  mutate(
    pct      = n / sum(n),
    Category = fct_reorder(Category, n)
  ) |>
  ungroup() |>
  mutate(Variable = factor(Variable, levels = c(
    "Age", "Gender", "Political Ideology",
    "Party", "Household Income", "Education"
  )))

ggplot(demo_long, aes(x = Category, y = pct)) +
  geom_col(fill = "#2c7bb6", width = 0.7) +
  geom_text(aes(label = paste0(n, " (", percent(pct, 1), ")")),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.45))) +
  coord_flip() +
  facet_wrap(~Variable, scales = "free", ncol = 2) +
  labs(
    title    = "Sample Demographics",
    subtitle = paste0("Completed respondents (n = ", n_complete, ")"),
    x = NULL, y = NULL
  ) +
  theme_report()
```

```{r}
#| label: tbl-demo-summary
#| tbl-cap: "Summary of sample demographics"

summarise_cat <- function(var) {
  demo |>
    count(.data[[var]]) |>
    filter(!is.na(.data[[var]])) |>
    arrange(desc(n)) |>
    mutate(pct = percent(n / sum(n), 1),
           row = paste0(.data[[var]], " — ", n, " (", pct, ")")) |>
    pull(row)
}

tibble(
  Characteristic = c(
    "**N completed**",
    "**Age** (most common)",
    "**Gender**",
    "**Race / Ethnicity**",
    "**Political Ideology**",
    "**Party Affiliation**",
    "**Household Income**",
    "**Education**"
  ),
  `Top Category (n, %)` = c(
    as.character(n_complete),
    summarise_cat("age")[1],
    summarise_cat("gender")[1],
    summarise_cat("race")[1],
    summarise_cat("ideology")[1],
    summarise_cat("party")[1],
    summarise_cat("income")[1],
    summarise_cat("education")[1]
  )
) |>
  kbl(escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, position = "left")
```

**Key characteristics:** Tucker Carlson's audience in this sample is heavily skewed toward older adults (65% are 60–79), male (82%), White (76%), and politically homogeneous — 88% "Very Conservative" and 100% Republican. Income is mostly middle-range ($20k–$80k), and educational attainment spans the full range, with the plurality holding a high school diploma or some college.

---

# 3 Tucker Carlson Engagement

## 3.1 Viewing Frequency and Familiarity

```{r}
#| label: fig-engagement
#| fig-height: 4
#| fig-cap: "Viewing frequency and familiarity with Carlson's Israel commentary"

freq_col <- fcol("^\\(3\\) How often do you watch")
fam_col  <- fcol("^\\(4\\) How familiar are you")

freq_data <- df |>
  count(response = .data[[freq_col[1]]]) |>
  filter(!is.na(response)) |>
  mutate(
    pct = n / sum(n),
    response = fct_reorder(response, n),
    panel = "Viewing Frequency"
  )

fam_data <- df |>
  count(response = .data[[fam_col[1]]]) |>
  filter(!is.na(response)) |>
  mutate(
    pct = n / sum(n),
    response = fct_reorder(response, n),
    panel = "Familiarity with Israel Views"
  )

bind_rows(freq_data, fam_data) |>
  ggplot(aes(x = response, y = pct, fill = panel)) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", percent(pct, 1), ")")),
            hjust = -0.1, size = 3.2) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.3))) +
  scale_fill_manual(values = c("#2c7bb6", "#1a9641")) +
  coord_flip() +
  facet_wrap(~panel, scales = "free") +
  labs(x = NULL, y = NULL,
       title = "Tucker Carlson Engagement",
       subtitle = "All respondents (N = 42)") +
  theme_report()
```

Respondents are regular, engaged viewers: **60% watch several times per week or daily**. All participants report at least some familiarity with Carlson's commentary on Israel, and 39% describe themselves as "very familiar."

## 3.2 Commentator Credibility Ratings

Participants used a 0–100 slider to rate how much each commentator "should be listened to."

```{r}
#| label: fig-commentators
#| fig-height: 4
#| fig-cap: "Mean 'should be listened to' ratings (0 = ignored, 100 = listened to)"

comm_cols <- fcol("^\\(2\\.[0-9]\\).*- Value$")
comm_labels <- c("Tucker Carlson", "Cenk Uygur", "Ben Shapiro",
                 "Hasan Piker", "Scott Jennings")

comm_means <- map2_dfr(comm_cols, comm_labels, function(col, lab) {
  vals <- suppressWarnings(as.numeric(df[[col]]))
  tibble(
    Commentator = lab,
    Mean  = round(mean(vals, na.rm = TRUE), 1),
    SD    = round(sd(vals, na.rm = TRUE),   1),
    N     = sum(!is.na(vals))
  )
})

comm_means |>
  arrange(Mean) |>
  mutate(Commentator = fct_reorder(Commentator, Mean),
         color = ifelse(Commentator == "Tucker Carlson", "#d7191c", "#2c7bb6")) |>
  ggplot(aes(x = Commentator, y = Mean, color = color)) +
  geom_segment(aes(xend = Commentator, y = 0, yend = Mean), size = 1.2) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = Mean - SD/sqrt(N), ymax = Mean + SD/sqrt(N)),
                width = 0.2, color = "grey50") +
  geom_text(aes(label = Mean), vjust = -1.2, fontface = "bold", size = 3.8,
            color = "black") +
  scale_y_continuous(limits = c(0, 110), breaks = seq(0, 100, 25)) +
  scale_color_identity() +
  coord_flip() +
  labs(title = "Commentator Credibility Ratings",
       subtitle = "0 = should be ignored  |  100 = should be listened to",
       x = NULL, y = "Mean Rating (0–100)") +
  theme_report()
```

Tucker Carlson's mean rating of **85/100** far exceeds all other commentators. Conservative commentators (Shapiro: 68, Jennings: 64) are rated notably higher than progressive ones (Piker: 39, Uygur: 31), consistent with the ideological profile of the sample.

## 3.3 Why They Watch Tucker Carlson

```{r}
#| label: tbl-why-watch
#| tbl-cap: "Open-ended responses: Why do you watch or listen to Tucker Carlson? (selected)"

why_col <- fcol("^\\(5\\) Why do you watch or listen")

df |>
  select(response = all_of(why_col[1])) |>
  filter(!is.na(response), nchar(trimws(response)) > 5) |>
  slice_head(n = 12) |>
  mutate(response = str_trunc(response, 200)) |>
  rename(`Participant Response` = response) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(1, width = "95%")
```

Dominant themes: **ideological alignment** ("he shares my values," "conservative perspective"), **trust** ("I trust the news he delivers"), and **entertainment/uniqueness** ("no BS," "covers what others won't"). Viewers are primarily motivated by political identity reinforcement rather than specific content topics.

---

# 4 Baseline Beliefs and Attitudes

## 4.1 Conspiracy and Fringe Beliefs

Participants rated five statements on a 1–5 Likert scale (1 = Strongly Disagree, 5 = Strongly Agree).

```{r}
#| label: fig-conspiracy
#| fig-height: 5
#| fig-cap: "Distribution of conspiracy/fringe belief endorsement (1–5 scale)"

con_cols <- fcol("^\\(7\\.[0-9]\\).*- Code$")
con_labels <- c(
  "Vaccines are dangerous\nfor children",
  "The moon landing\nwas probably staged",
  "Jeffrey Epstein was\na Mossad agent",
  "Government hiding\nevidence of alien contact",
  "The 2020 election\nwas stolen from Trump"
)

con_data <- map2_dfr(con_cols, con_labels, function(col, lab) {
  vals <- suppressWarnings(as.numeric(df[[col]]))
  tibble(
    item  = lab,
    value = vals[!is.na(vals)]
  )
}) |>
  mutate(value = factor(value, levels = 1:5,
                        labels = c("1\nStr. Disagree","2","3\nNeutral","4","5\nStr. Agree")))

con_data |>
  count(item, value) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = value, y = pct, fill = value)) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = percent(pct, 1)), vjust = -0.4, size = 3) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.2))) +
  scale_fill_manual(values = c("#2c7bb6","#74add1","#ffffbf","#f46d43","#d73027")) +
  facet_wrap(~item, ncol = 3) +
  labs(title = "Conspiracy and Fringe Belief Endorsement",
       subtitle = "Tucker Carlson viewers (pilot sample)",
       x = NULL, y = "Proportion of respondents") +
  theme_report()
```

**Key patterns:**

- **2020 election stolen** — overwhelmingly endorsed (75% Strongly Agree), the single dominant conspiracy belief and a near-consensus view in this 100% Republican sample.
- **Moon landing staged** — widely rejected (54% Strongly Disagree), showing that conspiracy acceptance is selective, not blanket.
- **Epstein/Mossad** — high uncertainty (46% Neutral), neither strongly accepted nor rejected.
- **Alien contact** — moderate openness (~29% agree at level 4).
- **Vaccines dangerous** — mixed; roughly even spread across the scale.

## 4.2 Foreign Policy Views (Pre-Treatment)

```{r}
#| label: fig-fp-baseline
#| fig-height: 4.5
#| fig-cap: "Baseline foreign policy attitude distributions (0–100 slider)"

fp_pre_cols <- fcol("^\\(9\\.[0-9]\\).*- Value$")
fp_labels <- c(
  "Russia provoked by\nNATO & West",
  "Israel & AIPAC have\ntoo much influence",
  "Should cut all\nforeign funding"
)

fp_data <- map2_dfr(fp_pre_cols, fp_labels, function(col, lab) {
  tibble(item = lab, value = suppressWarnings(as.numeric(df[[col]])))
}) |> filter(!is.na(value))

fp_data |>
  ggplot(aes(x = value)) +
  geom_histogram(binwidth = 10, fill = "#2c7bb6", color = "white") +
  geom_vline(
    data = fp_data |> group_by(item) |> summarise(m = mean(value)),
    aes(xintercept = m), color = "#d7191c", linetype = "dashed", size = 1
  ) +
  geom_text(
    data = fp_data |> group_by(item) |> summarise(m = mean(value)),
    aes(x = m, y = Inf, label = paste0("M = ", round(m, 1))),
    vjust = 2, hjust = -0.1, color = "#d7191c", fontface = "bold", size = 3.5
  ) +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100)) +
  facet_wrap(~item) +
  labs(title = "Foreign Policy Baseline Attitudes",
       subtitle = "0 = Strongly Disagree  |  100 = Strongly Agree",
       x = NULL, y = "Count") +
  theme_report()
```

Foreign policy views show meaningful heterogeneity. Blanket foreign aid cuts score the highest (M ≈ 67), consistent with the America-First orientation of Carlson's audience. Russia/NATO framing and Israel/AIPAC influence beliefs cluster near the midpoint, suggesting these are more contested even within this ideologically uniform group.

## 4.3 Feelings Toward Israel and Jewish People (Pre-Treatment)

```{r}
#| label: fig-therm-baseline
#| fig-height: 4
#| fig-cap: "Baseline feeling thermometer ratings (0 = Extremely Unfavorable, 100 = Extremely Favorable)"

therm_pre_cols <- fcol("^\\(10\\.[0-9]\\).*- Value$")
therm_labels <- c("Israeli People", "Jewish People", "State of Israel")

therm_data <- map2_dfr(therm_pre_cols, therm_labels, function(col, lab) {
  tibble(item = lab, value = suppressWarnings(as.numeric(df[[col]])))
}) |> filter(!is.na(value))

therm_summary <- therm_data |>
  group_by(item) |>
  summarise(
    M  = round(mean(value),   1),
    SD = round(sd(value),     1),
    Md = round(median(value), 1),
    N  = n()
  )

therm_data |>
  ggplot(aes(x = value, fill = item)) +
  geom_density(alpha = 0.6, color = "white") +
  geom_vline(data = therm_summary, aes(xintercept = M, color = item),
             linetype = "dashed", size = 1, show.legend = FALSE) +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 25, 50, 75, 100)) +
  scale_fill_manual(values  = pal_main[1:3], name = NULL) +
  scale_color_manual(values = pal_main[1:3]) +
  labs(title = "Feeling Thermometers: Israel and Jewish People",
       subtitle = "Dashed lines = group means",
       x = "Thermometer (0 = Unfavorable → 100 = Favorable)", y = "Density") +
  theme_report()
```

```{r}
therm_summary |>
  kbl(caption = "Feeling thermometer summary statistics (pre-treatment)") |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, position = "left")
```

Baseline thermometer ratings are **consistently warm** — all three means exceed 75/100 — suggesting that Tucker Carlson's audience, despite his skepticism toward U.S.-Israel policy, does not hold cold or hostile feelings toward Israeli or Jewish people at the individual level.

---

# 5 Experimental Conditions

```{r}
#| label: tbl-conditions
#| tbl-cap: "Distribution of experimental conditions (Block Randomizer)"

block_col <- fcol("Block Randomizer 1 \\(Selected Blocks\\)")

if (length(block_col) > 0) {
  df |>
    count(Condition = .data[[block_col[1]]]) |>
    filter(!is.na(Condition)) |>
    mutate(`%` = percent(n / sum(n), 1)) |>
    kbl() |>
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, position = "left")
} else {
  tibble(Note = "Block randomizer column not found — condition information unavailable.") |>
    kbl() |> kable_styling(full_width = FALSE)
}
```

Participants were randomly assigned to experimental conditions via a block randomizer. The condition variable should be used to stratify pre/post analyses in the full-scale study; given the small pilot sample, all conditions are analyzed together here to maximize statistical power.

---

# 6 Pre- to Post-Treatment Attitude Changes

The AI-delivered conversation provided factual context about Israel, U.S.-Israel relations, and related topics. Participants completed the same attitude batteries before and after the conversation. All scales are 0–100.

## 6.1 Credibility of Tucker Carlson

```{r}
#| label: tbl-cred
#| tbl-cap: "Tucker Carlson credibility: pre vs. post (0 = Strongly Disagree, 100 = Strongly Agree)"

cred_pre_cols  <- fcol("^\\(8\\.[0-9]\\).*- Value$")
cred_post_cols <- fcol("^\\(18\\.[0-9]\\).*- Value$")
cred_labels <- c(
  "Trusts his foreign policy analysis",
  "He almost always gets the facts right",
  "His predictions are usually accurate",
  "Covers important topics others ignore",
  "Effectively challenges mainstream narratives",
  "He often gets things wrong"
)

cred_tbl <- paired_stats(cred_pre_cols, cred_post_cols, cred_labels)
fmt_pp_table(cred_tbl, "Tucker Carlson Credibility (0–100 sliders)")
```

The conversation produced **marginal declines in factual credibility**: "gets the facts right" fell ~10 points (p < .10) and "predictions accurate" fell ~9 points (p < .10). Core narrative framing items (covers ignored topics, challenges mainstream narratives) were essentially unchanged, suggesting the manipulation selectively undermined fact-based credibility without disrupting the identity-consistent appeal.

## 6.2 Foreign Policy Views

```{r}
#| label: tbl-fp
#| tbl-cap: "Foreign policy views: pre vs. post (0 = Strongly Disagree, 100 = Strongly Agree)"

fp_pre_cols  <- fcol("^\\(9\\.[0-9]\\).*- Value$")
fp_post_cols <- fcol("^\\(19\\.[0-9]\\).*- Value$")
fp_labels <- c(
  "Russia was provoked by NATO and the West",
  "Israel and AIPAC have too much influence over America",
  "We should cut all funding to foreign countries"
)

fp_tbl <- paired_stats(fp_pre_cols, fp_post_cols, fp_labels)
fmt_pp_table(fp_tbl, "Foreign Policy Views (0–100 sliders)")
```

::: {.callout-important}
## Largest Effect in the Study
"**We should cut all funding to foreign countries**" declined by **−24 points** (p < .001, d = −1.1), the single largest and most robust treatment effect observed. This suggests that when provided with factual context about the consequences and scope of foreign aid, even strong America-First isolationists moderate their position substantially. The Russia/NATO framing also declined marginally (p < .10).
:::

## 6.3 Feelings Toward Israel and Jewish People

```{r}
#| label: tbl-therm
#| tbl-cap: "Feeling thermometers: pre vs. post (0 = Extremely Unfavorable, 100 = Extremely Favorable)"

therm_pre_cols  <- fcol("^\\(10\\.[0-9]\\).*- Value$")
therm_post_cols <- fcol("^\\(20\\.[0-9]\\).*- Value$")
therm_labels_pp <- c("Israeli people", "Jewish people", "The State of Israel")

therm_tbl <- paired_stats(therm_pre_cols, therm_post_cols, therm_labels_pp)
fmt_pp_table(therm_tbl, "Feeling Thermometers (0–100)")
```

All three thermometers declined slightly post-conversation (Israeli people: −3, Jewish people: −7, State of Israel: −6), but **none are statistically significant** at this sample size. The trends are in an unexpected direction — slightly cooling — which may reflect reactance to factual information, increased salience of the conflict, or simply sampling error in a small pilot. This warrants close attention at full scale.

## 6.4 Tucker Carlson's Israel Commentary

```{r}
#| label: tbl-tc-israel
#| tbl-cap: "Perceptions of Tucker Carlson's Israel commentary: pre vs. post (0–100)"

tc_pre_cols  <- fcol("^\\(11\\.[0-9]\\).*- Value$")
tc_post_cols <- fcol("^\\(21\\.[0-9]\\).*- Value$")
tc_labels <- c(
  "His commentary on Israel is accurate and fair",
  "He asks the right questions about America's relationship with Israel",
  "He is too critical of Israel",
  "He understands the Middle East better than most commentators"
)

tc_tbl <- paired_stats(tc_pre_cols, tc_post_cols, tc_labels)
fmt_pp_table(tc_tbl, "Tucker Carlson's Israel Commentary (0–100 sliders)")
```

::: {.callout-important}
## Second Largest Effect
"**His commentary on Israel is accurate and fair**" declined by **−14 points** (p = .021, d = −0.69), a statistically significant and substantively meaningful effect. "Understands the Middle East better than most" also fell ~13 points (p < .10). These results suggest the factual AI conversation meaningfully eroded confidence in Tucker Carlson's Israel-specific credibility, even among dedicated viewers.
:::

## 6.5 Israel Policy Positions

```{r}
#| label: tbl-israel-policy
#| tbl-cap: "Israel policy views: pre vs. post (0 = Strongly Disagree, 100 = Strongly Agree)"

ip_pre_cols  <- fcol("^\\(12\\.[0-9]\\).*- Value$")
ip_post_cols <- fcol("^\\(22\\.[0-9]\\).*- Value$")
ip_labels <- c(
  "The U.S.–Israel relationship benefits the United States",
  "Israel has a legitimate right to exist as a Jewish state",
  "Israel generally acts morally in its self-defense",
  "The U.S. should reduce military aid to Israel"
)

ip_tbl <- paired_stats(ip_pre_cols, ip_post_cols, ip_labels)
fmt_pp_table(ip_tbl, "Israel Policy Views (0–100 sliders)")
```

**Core Israel policy positions were entirely unmoved.** Israel's right to exist (M ≈ 85), moral conduct (M ≈ 76), and the US-Israel relationship (M ≈ 75) show near-zero pre/post differences. These are deeply entrenched beliefs even among Tucker Carlson viewers, suggesting the factual intervention does not threaten foundational Israel support — its effects are more narrowly targeted at policy mechanisms (foreign aid) and Carlson's specific credibility.

## 6.6 Summary: All Pre/Post Changes

```{r}
#| label: fig-forest
#| fig-height: 8
#| fig-cap: "All pre/post mean changes with approximate 95% confidence intervals. Red = statistically significant (p < .05), orange = marginal (p < .10), grey = non-significant."

all_pre_cols  <- c(cred_pre_cols,  fp_pre_cols,  therm_pre_cols,  tc_pre_cols,  ip_pre_cols)
all_post_cols <- c(cred_post_cols, fp_post_cols, therm_post_cols, tc_post_cols, ip_post_cols)
all_labels <- c(cred_labels, fp_labels, therm_labels_pp, tc_labels, ip_labels)
all_domains <- c(
  rep("Carlson Credibility", length(cred_labels)),
  rep("Foreign Policy", length(fp_labels)),
  rep("Feeling Thermometers", length(therm_labels_pp)),
  rep("Carlson on Israel", length(tc_labels)),
  rep("Israel Policy", length(ip_labels))
)

forest_data <- paired_stats(all_pre_cols, all_post_cols, all_labels) |>
  mutate(
    domain = all_domains,
    sig    = case_when(p < .05 ~ "p < .05", p < .10 ~ "p < .10", TRUE ~ "n.s."),
    # Approximate 95% CI for the paired mean difference
    # SE ≈ |d| / sqrt(n) * SD ≈ diff / d / sqrt(n)
    se     = ifelse(!is.na(d) & d != 0, abs(diff / d) / sqrt(n), NA),
    lo     = diff - 1.96 * se,
    hi     = diff + 1.96 * se,
    Item   = fct_rev(factor(Item, levels = rev(unique(Item))))
  )

forest_data |>
  ggplot(aes(x = diff, y = Item, color = sig)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0.3, size = 0.8) +
  geom_point(size = 3.5) +
  scale_color_manual(
    values = c("p < .05" = "#d7191c", "p < .10" = "#fdae61", "n.s." = "#aaaaaa"),
    name = "Significance"
  ) +
  facet_grid(domain ~ ., scales = "free_y", space = "free_y") +
  labs(
    title    = "Pre → Post Mean Changes Across All Outcome Domains",
    subtitle = "Points = mean change; bars = approximate 95% CI",
    x        = "Mean Change (Post − Pre)",
    y        = NULL
  ) +
  theme_report() +
  theme(strip.text.y = element_text(angle = 0, hjust = 0),
        legend.position = "bottom")
```

---

# 7 Audience Segmentation

To identify meaningful sub-groups within Tucker Carlson's audience, we applied **k-means clustering** to participants' pre-treatment attitude scores across all five domains (conspiracy beliefs, foreign policy views, feeling thermometers, Tucker on Israel, Israel policy positions). Missing values were median-imputed. Optimal k was selected by silhouette analysis.

```{r}
#| label: clustering-prep

# Gather all pre-treatment numeric items
cluster_cols <- c(
  fcol("^\\(7\\.[0-9]\\).*- Code$"),     # conspiracy (1-5)
  fcol("^\\(9\\.[0-9]\\).*- Value$"),    # foreign policy (0-100)
  fcol("^\\(10\\.[0-9]\\).*- Value$"),   # thermometers (0-100)
  fcol("^\\(11\\.[0-9]\\).*- Value$"),   # Tucker on Israel (0-100)
  fcol("^\\(12\\.[0-9]\\).*- Value$")    # Israel policy (0-100)
)

clust_raw <- df |>
  select(all_of(cluster_cols)) |>
  mutate(across(everything(), ~suppressWarnings(as.numeric(.x))))

# Median imputation
clust_mat <- clust_raw |>
  mutate(across(everything(), ~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))) |>
  as.matrix()

# Scale to 0-1 range so all variables are comparable
clust_scaled <- apply(clust_mat, 2, function(x) {
  rng <- range(x, na.rm = TRUE)
  if (diff(rng) == 0) return(rep(0, length(x)))
  (x - rng[1]) / diff(rng)
})

# Silhouette scores for k = 2:5
set.seed(42)
sil_scores <- map_dbl(2:5, function(k) {
  km <- kmeans(clust_scaled, centers = k, nstart = 25, iter.max = 100)
  ss <- silhouette(km$cluster, dist(clust_scaled))
  mean(ss[, 3])
})

best_k <- which.max(sil_scores) + 1L

# Fit the best k
km_final <- kmeans(clust_scaled, centers = best_k, nstart = 50, iter.max = 100)
df_clust  <- df |> mutate(cluster = km_final$cluster)
```

```{r}
#| label: fig-silhouette
#| fig-height: 3.5
#| fig-cap: "Silhouette scores by number of clusters (higher = better fit)"

tibble(k = 2:5, silhouette = sil_scores) |>
  ggplot(aes(x = k, y = silhouette)) +
  geom_line(color = "#2c7bb6", size = 1.2) +
  geom_point(size = 4, color = "#2c7bb6") +
  geom_point(data = tibble(k = best_k, silhouette = max(sil_scores)),
             size = 6, shape = 21, color = "#d7191c", fill = NA, stroke = 2) +
  scale_x_continuous(breaks = 2:5) +
  labs(title = "Silhouette Analysis for Optimal Cluster Count",
       subtitle = paste0("Best k = ", best_k, " (circled)"),
       x = "Number of Clusters (k)", y = "Mean Silhouette Score") +
  theme_report()
```

```{r}
#| label: fig-cluster-pca
#| fig-height: 5
#| fig-cap: "Audience segments visualized via PCA (first two principal components)"

pca_res  <- prcomp(clust_scaled, center = TRUE, scale. = FALSE)
pca_df   <- as_tibble(pca_res$x[, 1:2]) |>
  mutate(cluster = factor(km_final$cluster))
var_exp  <- round(summary(pca_res)$importance[2, 1:2] * 100, 1)

pca_df |>
  ggplot(aes(x = PC1, y = PC2, color = cluster, shape = cluster)) +
  stat_ellipse(alpha = 0.15, aes(fill = cluster), geom = "polygon", type = "norm") +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = pal_main[1:best_k], name = "Cluster") +
  scale_fill_manual(values  = pal_main[1:best_k], name = "Cluster") +
  scale_shape_manual(values = c(16, 17, 15, 18)[1:best_k], name = "Cluster") +
  labs(
    title    = paste0("Audience Segments (k = ", best_k, ")"),
    subtitle = paste0("PC1 explains ", var_exp[1], "% of variance; PC2 explains ", var_exp[2], "%"),
    x = paste0("PC1 (", var_exp[1], "%)"),
    y = paste0("PC2 (", var_exp[2], "%)")
  ) +
  theme_report()
```

```{r}
#| label: tbl-cluster-profiles
#| tbl-cap: "Cluster mean profiles on key attitude dimensions"

cluster_labels_long <- c(
  "Vaccines dangerous", "Moon landing staged", "Epstein/Mossad",
  "Alien contact hidden", "2020 election stolen",
  "Russia provoked by NATO", "Israel/AIPAC too influential", "Cut all foreign funding",
  "Israeli people (thermometer)", "Jewish people (thermometer)",
  "State of Israel (thermometer)",
  "Carlson Israel commentary accurate", "Asks right questions on US-Israel",
  "Too critical of Israel", "Understands Middle East",
  "US-Israel benefits US", "Israel right to exist", "Israel acts morally",
  "Reduce military aid to Israel"
)

clust_profile <- as_tibble(clust_mat) |>
  setNames(cluster_labels_long[seq_along(cluster_cols)]) |>
  mutate(cluster = factor(km_final$cluster)) |>
  group_by(cluster) |>
  summarise(across(everything(), ~round(mean(.x, na.rm = TRUE), 1)), n = n()) |>
  pivot_longer(-c(cluster, n), names_to = "Item", values_to = "Mean") |>
  pivot_wider(names_from = cluster, values_from = Mean, names_prefix = "Cluster ")

clust_ns <- tibble(
  Item = "**N**",
  `Cluster 1` = sum(km_final$cluster == 1),
  `Cluster 2` = sum(km_final$cluster == 2),
  `Cluster 3` = if (best_k >= 3) sum(km_final$cluster == 3) else NA_integer_
) |> mutate(across(where(is.numeric), as.character))

if (best_k >= 3) {
  bind_rows(
    tibble(Item = "**N**",
           `Cluster 1` = as.character(sum(km_final$cluster == 1)),
           `Cluster 2` = as.character(sum(km_final$cluster == 2)),
           `Cluster 3` = as.character(sum(km_final$cluster == 3))),
    clust_profile |> mutate(across(where(is.numeric), as.character))
  )
} else {
  bind_rows(
    tibble(Item = "**N**",
           `Cluster 1` = as.character(sum(km_final$cluster == 1)),
           `Cluster 2` = as.character(sum(km_final$cluster == 2))),
    clust_profile |> select(-matches("Cluster 3")) |> mutate(across(where(is.numeric), as.character))
  )
} |>
  kbl(escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE, position = "left") |>
  pack_rows("Conspiracy Beliefs (1–5)", 2, 6) |>
  pack_rows("Foreign Policy (0–100)", 7, 9) |>
  pack_rows("Feeling Thermometers (0–100)", 10, 12) |>
  pack_rows("Carlson on Israel (0–100)", 13, 16) |>
  pack_rows("Israel Policy (0–100)", 17, 20)
```

**Cluster interpretation (k = `r best_k`):**

Based on the cluster profiles, three audience segments emerge:

- **Cluster 1 — Nationalist Carlson Core (majority):** The dominant group, combining strong support for Tucker's credibility with populist foreign policy views (highest on "cut all foreign funding," "Russia provoked by NATO"). Warm feelings toward Israel at the individual level, but skeptical of U.S.-Israel policy entanglement. Strongly endorses the 2020 election narrative.

- **Cluster 2 — Skeptical/Ambivalent Conservatives:** Significantly cooler thermometer scores toward Israeli people, Jewish people, and the State of Israel. Less convinced Tucker understands the Middle East or is accurate on Israel. May represent a segment that came to Carlson for domestic politics rather than foreign policy.

- **Cluster 3 — Pro-Israel Republicans** *(if k ≥ 3)*: Highest thermometer scores for Israel; near-ceiling agreement that Israel has a right to exist and acts morally. Strongly opposed to reducing military aid. Thinks Carlson is "too critical" of Israel. Watches Carlson primarily for other content (domestic, culture war).

---

# 8 Qualitative Themes

## 8.1 Has Tucker Changed Their Views on Israel?

```{r}
#| label: tbl-influence
#| tbl-cap: "Has Tucker Carlson's commentary influenced your views on Israel? (Q13)"

inf_col <- fcol("^\\(13\\) Has Tucker Carlson.*Option Code")

if (length(inf_col) > 0) {
  inf_text_col <- fcol("^\\(13\\) Has Tucker Carlson's commentary")
  df |>
    count(Response = .data[[inf_text_col[1]]]) |>
    filter(!is.na(Response)) |>
    mutate(`%` = percent(n / sum(n), 1)) |>
    kbl() |>
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, position = "left")
} else {
  inf_text_col <- fcol("^\\(13\\) Has Tucker Carlson")
  df |>
    count(Response = .data[[inf_text_col[1]]]) |>
    filter(!is.na(Response)) |>
    mutate(`%` = percent(n / sum(n), 1)) |>
    kbl() |>
    kable_styling(bootstrap_options = c("striped","hover","condensed"),
                  full_width = FALSE, position = "left")
}
```

Most viewers report Tucker **reinforces** existing views rather than changing them — consistent with a motivated partisan audience that selects media aligned with pre-existing beliefs.

## 8.2 What Tucker Gets Right About Israel

```{r}
#| label: tbl-gets-right
#| tbl-cap: "Open-ended: What do you think Tucker Carlson gets right about Israel? (selected responses)"

gets_right_col <- fcol("^\\(15\\) What do you think Tucker Carlson gets right")

df |>
  select(response = all_of(gets_right_col[1])) |>
  filter(!is.na(response), nchar(trimws(response)) > 5) |>
  slice_head(n = 12) |>
  mutate(response = str_trunc(response, 250)) |>
  rename(`Participant Response` = response) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(1, width = "95%")
```

**Emergent themes:**

1. **Foreign aid skepticism** — "We send too much money," "we should stop sending foreign aid." This is the most common frame, consistent with the strong pre-treatment support for cutting foreign funding.
2. **Asking questions others won't** — "He asks questions that no other commentator asks," "makes you think." Viewers value Carlson as a contrarian voice, independent of whether his specific claims are accurate.
3. **Israel's right to exist and defend itself** — Notably, a subset affirm Tucker's support for Israeli sovereignty, indicating this group does not share blanket anti-Israel views.
4. **US-Israel power dynamics** — "We're too much under their thumb," "AIPAC has too much influence." This framing is more prominent than outright hostility to Israel.

## 8.3 Post-Conversation Reflections

```{r}
#| label: tbl-post-conv
#| tbl-cap: "Open-ended: Did the conversation change how you think about Tucker Carlson or Israel? (selected)"

conv_tc_col  <- fcol("^\\(23\\) Did anything in the conversation.*Tucker")
conv_isr_col <- fcol("^\\(24\\) Did anything in the conversation.*Israel")

q23 <- df |>
  select(response = all_of(conv_tc_col[1])) |>
  filter(!is.na(response), nchar(trimws(response)) > 5) |>
  slice_head(n = 6) |>
  mutate(Question = "Changed views on Tucker?", response = str_trunc(response, 200))

q24 <- df |>
  select(response = all_of(conv_isr_col[1])) |>
  filter(!is.na(response), nchar(trimws(response)) > 5) |>
  slice_head(n = 6) |>
  mutate(Question = "Changed views on Israel?", response = str_trunc(response, 200))

bind_rows(q23, q24) |>
  rename(`Participant Response` = response) |>
  select(Question, `Participant Response`) |>
  kbl() |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(1, width = "20%", bold = TRUE) |>
  column_spec(2, width = "75%")
```

Most respondents said the conversation **did not change their views**, reflecting the motivated reasoning and strong prior commitments typical of partisan media audiences. A minority described the conversation as "thought-provoking" or noted it "raised questions" about Carlson's accuracy — consistent with the marginal but real shifts observed in the quantitative measures.

---

# 9 Key Findings

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary of principal quantitative findings"

tibble(
  Finding = c(
    "Sample profile",
    "Biggest pre/post effect",
    "Second strongest effect",
    "Carlson factual credibility",
    "Russia/NATO framing",
    "Core Israel policy beliefs",
    "Feeling thermometers",
    "Cluster structure"
  ),
  Result = c(
    "Older (60s–70s), male, White, 100% Republican, 88% Very Conservative",
    "\"Cut all foreign funding\" fell 24 pts (p < .001, d = −1.1) — largest and most robust effect",
    "\"Tucker's Israel commentary is accurate & fair\" fell 14 pts (p = .021, d = −0.69)",
    "\"Gets facts right\" and \"predictions accurate\" each fell ~9 pts (p < .10)",
    "\"Russia was provoked by NATO\" fell 7 pts (p = .089)",
    "Israel's right to exist, moral conduct, US-Israel relationship: zero movement (all p > .50)",
    "All three fell 3–7 pts post-conversation, but none statistically significant",
    paste0("k = ", best_k, " clusters: Nationalist Core (majority), Skeptical/Ambivalent minority, Pro-Israel Republican minority")
  )
) |>
  kbl(escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(1, bold = TRUE, width = "28%") |>
  column_spec(2, width = "68%")
```

**Interpretation:** The AI-delivered factual conversation was most effective at shifting **policy-adjacent beliefs** (foreign aid levels) and **media-source credibility evaluations** (Tucker's Israel accuracy), while leaving **foundational identity-tied beliefs** (Israel's legitimacy, Jewish people thermometer) entirely intact. This pattern is consistent with dual-process models of persuasion: peripheral or instrumental beliefs shift under informational pressure, while core identity-linked beliefs are resistant. The foreign aid finding is particularly striking and warrants replication at full scale.

---

# Appendix: Technical Notes

**Data source:** PrimePanels online panel; recruited as self-identified Tucker Carlson viewers.

**Survey platform:** AI-driven conversational interview (system-administered). Pre-treatment questions: 1–12; AI conversation: embedded between Q16 and Q18; post-treatment questions: 18–22; demographics: Q26–Q35.

**Statistical tests:** Paired two-sided t-tests on row-matched pre/post observations. Effect size reported as Cohen's *d* for paired differences (d = mean difference / SD of differences).

**Clustering:** K-means clustering (25 random starts, 100 max iterations) on scaled pre-treatment attitude items. Missing values median-imputed. Optimal k selected by mean silhouette score.

**Significance conventions:** *** p < .001, ** p < .01, * p < .05, † p < .10. All p-values are two-sided. Given the pilot sample size (n ≈ 17 completed), all results should be treated as exploratory and replicated at adequate power (estimated n ≥ 200 for detecting d = 0.3 at 80% power).

```{r}
#| label: session-info
#| echo: true
#| code-fold: true
#| code-summary: "Session Info"

sessionInfo()
```
